---
title: "Data Analyst Presentation"
output: html_document
date: "2023-03-27"
---

# Load libraries 
```{r}
library(readr)
library(ggplot2)
library(dplyr)
```

#Import Dataset
```{r}
Clibrary(readr)
df <- read_csv("OneDrive/Data Science/Projects/COVID-19 Stat Aanalysis /data_mexico_400_145_22.csv")
View(df)
head(df)
```

# Research Question: 
Are Age and BMI significant predictors of the number of days from symptom onset to admission? 

# Variables:
  IV: Age & BMI_Category # Continuous & Categorical
  DV: Days_sympt_admiss- #Continuous

# Hypothesis
H0: Combined, age and BMI do not explain variation in the number for days from symptom 
  onset to admission. 

H1: Combined, age and BMI do explain variation in the number for days from symptom 
onset to admission. 

H0Age: Age does not explain variation in the number for days from symptom 
onset to admission. 
H1Age: Age does explain variation in the number for days from symptom 
onset to admission. 

H0BMI: BMI does explain variation in the number for days from symptom 
onset to admission. 
H1BMI: BMI does explain variation in the number for days from symptom 
onset to admission. 

#Data Exploration
# Missing Values: 
#Age
```{r}
summary(df$Age)
count(filter(df, df$Age == '9999'))
df1 <- subset(df, !(df$Age == '9999')) # 5 missing values removed
```

#BMI
```{r}
summary(df1$BMI)
table(df1$BMI)
```

# Days_sympt_admiss
```{r}
summary(df1$Days_sympt_admiss)
table(df1$Days_sympt_admiss)
```
# Scatter-plot:

# Age ~ Days_sympt_admiss
```{r}
qplot(x = Age, y = Days_sympt_admiss, data = df1) + geom_smooth(method = lm, formula = y ~ x)
```

# BMI ~ Days_sympt_admiss
```{r}
qplot(x = BMI, y = Days_sympt_admiss, data = df1) + geom_smooth(method = lm, formula = y ~ x)
```

# Build a regression model
```{r}
model1 <- lm(df1$Days_sympt_admiss~ df1$Age+ df1$BMI, data = df1)
```

# Assess the model
```{r}
summary(model1)
plot(model1, which = 1)
plot(model1, which = 2)
```








